---
title: "Beaufort Lagoon source waters - poster"
author: "Christina Bonsell and Emily Bristol"
date: "Jan 18, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(cowplot)
library(DT)
library(knitr)
library(kableExtra)
library(plotly)
library(leaflet)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
YSI <- read_csv("All_BLE_Sonde_Data_2018_2019.csv", col_types = cols(date_time = col_date(format = "%m/%d/%Y"))) %>% 
  rename(Date_collected=date_time)
#note; changed date of summer 2019 STL bc times near midnight and YSI was technically collected on a diff day than 18O
YSI$water_column_position[is.na(YSI$water_column_position)] <- "surface"

O18 <- read_csv("BLE LTER 18O.csv", col_types = cols(Date_collected = col_date(format = "%m/%d/%Y"))) %>% 
  arrange(Date_collected, Station)
O18$WaterColumnDepth[is.na(O18$WaterColumnDepth)] <- "surface"

ctd <- read.csv("derived_BLE_insituCTD_2018to2019.csv") %>% 
  mutate(date = as.Date(date_time), Station= station)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
input <- left_join(O18,YSI, by=c("Station"="station","Date_collected","WaterColumnDepth"="water_column_position")) %>% 
  select(Node, Drainage, Lagoon, Station, Date_collected, DepthCat=WaterColumnDepth, Sal=sal, delta_18O) %>% 
  mutate(Season=case_when(month(Date_collected)==7|month(Date_collected)==8 ~ "Summer",
                          month(Date_collected)==6 ~ "Break-up",
                          month(Date_collected)==4 ~ "Under-ice"),
         Habitat= case_when(grepl("R", Station) ~ "River",
                            grepl("D", Station) ~ "Deep",
                            TRUE ~"Shallow")) %>% 
  drop_na(Station)


input$DepthCat <- factor(input$DepthCat, levels=c("surface","bottom"), 
                         labels=c("surface (<0.3 m)","near-bottom"))
input$Habitat <- factor(input$Habitat, levels=c("River","Shallow","Deep"))
input$Lagoon <- factor(input$Lagoon, levels=c("Elson","Simps","Stef","Kakto","Jago"))
input$Drainage <- factor(input$Drainage, levels=c("Elson_W","Elson_E","Simps","Stef","Kakto","Jago"),
                         labels=c("Elson West", "Elson East", "Simpson", "Stefansson", "Kaktovik", "Jago"))
input$Station <- factor(input$Station, levels=c("AVR1","MYR1","NNR1",
                                            "EWLS1","EWLS2","EWLD1","EWLD2",
                                            "EELS1","EELS2","EELD1","EELD2",
                                            "KUR1","SILS1","SILS2","SILD1","SILD2",
                                            "SAR1","STLS1","STLS2","STLD1","STLD2",
                                            "KALS1","KALS2","KALD1","KALD2",
                                            "JAR1","JALS1","JALS2","JALD1","JALD2"))

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

Pal <- c('#625989', '#636591', '#657298', '#677f9f', '#6a8ba5', '#6e98aa', '#72a4ae', '#78b1b1', '#80bdb2', '#8ac9b0', '#96d6ac', '#a4e1a4', '#b7ed95', '#cef879', '#e4f361', '#cce75b', '#b8da55', '#a7cc4f', '#9abd48', '#91ae41', '#8a9f39', '#868f32', '#847e2a', '#836d21', '#835b19', '#834710', '#842f08', '#840000')

```

###The Beaufort Lagoon Ecosystems Long-Term Ecological Research program ([BLE LTER](ble.lternet.edu)) samples lagoons and coastal areas across the Beaufort Sea coast


###We have 4 stations per lagoon system, two in shallow reaches of the lagoon (<1m), and two in deeper areas (>2.5m). We also sample major freshwater inflows associated with each lagoon. 

```{r map, echo=F, message=F, warnings=F, fig.height=4}
Stations <- read_csv("BLE_LTER_CP_Stations.csv", 
                     col_types=cols(
  StationId = col_character(),
  StationName = col_character(),
  Latitude = col_double(),
  Longitude = col_double(),
  Habitat = col_character(),
  Type = col_factor()
)) %>% 
  filter(Type!="ocean")

pal <- colorFactor(c("gold", "navy", "chartreuse3"), domain = c("primary", "secondary", "river"))

Stations %>% leaflet() %>% 
  addProviderTiles(providers$Esri.WorldImagery) %>% 
  addCircleMarkers(~ Longitude, ~ Latitude,
                   group = "StationName",
                   color = ~pal(Type),
                   radius=6,
                   stroke = FALSE, 
                   fillOpacity = 0.5,
                   label= ~StationName,
                   labelOptions = labelOptions(permenant = T,
                                               direction = 'right',
                                               offset=c(0,-5),
                                               opacity=1,
                                               style = list(
                                                 "font-style" = "bold",
                                                 "font-size" = "14px",
                                                 "color"="white",
                                                 "background"="transparent",
                                                 "border"="none",
                                                 "box-shadow"="none"))) %>% 
  addLegend(pal = pal, values = ~Type, opacity = 1, title="Station type", group="StationPoint") %>% 
  addScaleBar() %>% 
  addMiniMap(zoomLevelFixed = 2, 
             centerFixed=c(65, -150))
```


###These lagoons exhibit large variability in **salinity** over the year.

(no data for EELD1)

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=4}
mytheme <-theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12),
        axis.text.y=element_text(size=14),
        axis.title=element_text(size=16))


ctd %>% 
  filter(station!="EELD1", flags_condsal!="INV") %>% 
  group_by(station, date) %>% 
  summarize(mSal=mean(salinity, na.rm=T))%>%  
  ggplot(aes(date, mSal))+
  geom_line(size=1)+
  facet_wrap(~station, nrow=2, drop=F)+
  theme_minimal_hgrid(12)+
  ylim(c(0,45))+
  ylab("Salinity")+
  xlab("")+
  scale_x_date(breaks="2 months", date_labels="%b")+
  mytheme
```

##What causes this?

###To find out, we used salinity and $\delta ^{18}O$ of lagoon waters sampled in April (full sea ice cover), June (sea ice break-up), and August (open water summer). Explore the data in the plot below:

```{r, echo=FALSE, message=FALSE, warning=FALSE,}
plotdat <- ungroup(input) %>% filter(Habitat!="River")

inputplot <- ggplot(plotdat, aes(Sal, delta_18O, color=DepthCat, fill=Season, group=Station))+
  geom_point(shape=21, size=2, alpha=0.8)+
  scale_fill_manual(values=Pal[c(1,10,20)])+
  scale_color_manual(values=c("grey","black"))+
  scale_y_continuous(breaks=seq(-24,-4,4))+
  theme_minimal()+
  facet_wrap(~Lagoon)+
  xlab("Salinity")+
  labs(shape="Sampling Depth")

p <- ggplotly(inputplot, tooltip=c("Sal","delta_18O","Station")) 
p

```


###We used the distinct salinity and $\delta ^{18}O$ values of sea ice melt (SIM), marine Polar Mixed Layer (PML), and meteoric water (MW) to determine the relative contribution of each endmember to these dynamic lagoons.

### $\delta ^{18}O$ of MW actually varies longitudinally, as seen by the pattern in freshwater inflow samples, here with stations ordered west->east:

```{r riverO, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=5}
rivplot <- input %>% filter (Habitat=="River") %>% 
  mutate(Station = recode(Station, AVR1="Avak Cr.", MYR1="Mayo. R.", NNR1="unkn R.",
         KUR1="Kup. R.", SAR1= "Sag. R.", JAR1="Jago R.")) %>% 
  ggplot(aes(Station,delta_18O))+
  geom_point(aes(color=Season), size=3)+
  scale_color_manual(values=Pal[c(1,20)])+
  facet_grid(.~Lagoon, scales="free")+
  theme_cowplot()+
  ylab(~ paste(delta ^ 18, "O ", ("%"[0])))+
  xlab("")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

rivplot


#add ave river value as column
riv_vals <- input %>% filter (Habitat=="River") %>% 
  group_by(Lagoon) %>% 
  summarize(riv_d18O=mean(delta_18O), sd=sd(delta_18O))

#Make kable
kable(riv_vals, digits=2) %>% 
  kable_styling(full_width=F, position="left")

input <- left_join(input,riv_vals) %>% 
  select(-sd) 

input$riv_d18O[input$Lagoon=="Kakto"] <-  -21.4

```

###We solved the following system of equations for each lagoon water sample:


$SIM+MW+PML = 1$

$5*SIM + 0*MW + 32.1*PML =  Salinity$ 

$-2*SIM + x*MW + -3.5*PML = \delta ^{18}O$

where $x$ is the mean value for rivers associated with a particular lagoon (see above table)

```{r create_function, echo=FALSE, message=FALSE, warning=FALSE}

calc_source <- function(S, O, mw){
  
  A <- matrix(data=c(1, 1, 1, 5, 0, 32.1, -2, mw, -3.5), nrow=3, ncol=3, byrow=TRUE)    
  B <- matrix(data=c(1, S, O), nrow=3, ncol=1, byrow=FALSE)
  
  x <- round(solve(A, B), 3)

  return(x)
}

```

```{r calculate_fractions, echo=FALSE, message=FALSE, warning=FALSE}

sources <- matrix(ncol=3, nrow=nrow(input))
for(i in 1:nrow(input)){
  sources[i,] <- calc_source(input$Sal[i], input$delta_18O[i], input$riv_d18O[i])
}

a <- as.data.frame(sources)

colnames(a)=c("SIM","MW","PML")

data <- bind_cols(input,a)


```

```{r for_plot, echo=FALSE, message=FALSE, warning=FALSE}
a2 <- as.data.frame(a, col.names=c("SIM","MW","PML"))

colnames(a2)=c("SIM","MW","PML")

data2 <- bind_cols(input,a2) %>% 
  pivot_longer(cols=SIM:PML, names_to = "Source")

```

```{r means, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8, fig.width=11}
data_means <- bind_cols(input,a2) %>% 
  pivot_longer(cols=SIM:PML, names_to = "Source") %>% 
  group_by(Lagoon, Drainage, Station, DepthCat, Habitat, Season, Source, delta_18O, Sal) %>% 
  summarize(mFrac=mean(value, na.rm=T), sdFrac=sd(value, na.rm=T), mDate=mean(Date_collected))

```

#The results of our mixing model (below) show how source waters stratify and/or mix in each lagoon over the year. 

##There are some interesting differences between lagoons, for example:

* Elson West at break up has runoff throughout the water column, while other stations are very stratified.
* Unexpected runoff water (MW) in surface waters of Stefansson Sound under the sea ice in April, due to a warm March in the upper reaches of the Sagavanirktok River watershed.
* Relatively little contribution by sea ice melt (SIM) in Stefansson Sound during our sampling periods

###Note that summer 2019 was a very low sea ice year for the Beaufort Sea, which may be reflected in the low proportion of sea ice melt water during summer in the lagoons.


Error bars are SD. Values beyond 100 are due to hypersalinity in the winter, caused by brine exclusion during sea ice formation. This causes salinity to go beyond the end-member value. 


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=9}
drain_means <- bind_cols(input,a2) %>% 
  pivot_longer(cols=SIM:PML, names_to = "Source") %>% 
  filter(Habitat!="River", !is.na(Drainage)) %>% 
  group_by(Drainage, DepthCat,Season, Source) %>% 
  summarize(mFrac=mean(value, na.rm=T), sdFrac=sd(value, na.rm=T), mDate=mean(Date_collected)) %>% 
  mutate(ci_l=mFrac-sdFrac, ci_u=mFrac+sdFrac)


drain_means$DepthCat = with(drain_means, factor(DepthCat, levels = rev(levels(DepthCat))))

#change confidence interval location to go with stacked barplot
drain_means$ci_l[drain_means$Source == "PML"] <- with(drain_means,ci_l[Source == "PML"] +
                                                        ci_l[Source == "MW"])
drain_means$ci_u[drain_means$Source == "PML"] <- with(drain_means,ci_u[Source == "PML"] +
                                                        ci_u[Source == "MW"])
drain_means$ci_l[drain_means$Source == "SIM"] <- ifelse(drain_means$mFrac[drain_means$Source=="SIM"]<0, 0,
                                                        with(drain_means,ci_l[Source == "PML"] +ci_l[Source == "SIM"]))
drain_means$ci_u[drain_means$Source == "SIM"] <- ifelse(drain_means$mFrac[drain_means$Source=="SIM"]<0, 0,
                                                        with(drain_means,ci_u[Source == "PML"] + ci_u[Source == "SIM"]))


drain_means %>% 
  ggplot(aes(DepthCat, mFrac*100))+
  geom_col(aes(fill = Source), position = position_stack(reverse = T)) +
  scale_fill_manual(values=c('#84c64d', '#409e93', '#4e6cb2'))+
  geom_errorbar(aes(ymin = ci_l*100, ymax = ci_u*100), width=0, 
                stat="identity")+
  coord_flip(ylim=c(0,100)) +
  geom_hline(yintercept=c(0,100))+
  facet_grid(Drainage~Season, scales="free")+
  theme_cowplot()+
  ylab("% Contribution")+
  xlab("")+
  theme(strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10))

```

## We can also divide results into different areas of each lagoon:


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6}
drain_means_shallow <- bind_cols(input,a2) %>% 
  pivot_longer(cols=SIM:PML, names_to = "Source") %>% 
  filter(Habitat=="Shallow", !is.na(Drainage)) %>% 
  group_by(Drainage, DepthCat,Season, Source) %>% 
  summarize(mFrac=mean(value, na.rm=T), sdFrac=sd(value, na.rm=T), mDate=mean(Date_collected)) %>% 
  mutate(ci_l=mFrac-sdFrac, ci_u=mFrac+sdFrac)


drain_means_shallow$DepthCat = with(drain_means_shallow, factor(DepthCat, levels = rev(levels(DepthCat))))

#change confidence interval location to go with stacked barplot
drain_means_shallow$ci_l[drain_means_shallow$Source == "PML"] <- with(drain_means_shallow,ci_l[Source == "PML"] +
                                                        ci_l[Source == "MW"])
drain_means_shallow$ci_u[drain_means_shallow$Source == "PML"] <- with(drain_means_shallow,ci_u[Source == "PML"] +
                                                        ci_u[Source == "MW"])
drain_means_shallow$ci_l[drain_means_shallow$Source == "SIM"] <- ifelse(drain_means_shallow$mFrac[drain_means_shallow$Source=="SIM"]<0, 0,
                                                        with(drain_means_shallow,ci_l[Source == "PML"] +ci_l[Source == "SIM"]))
drain_means_shallow$ci_u[drain_means_shallow$Source == "SIM"] <- ifelse(drain_means_shallow$mFrac[drain_means_shallow$Source=="SIM"]<0, 0,
                                                        with(drain_means_shallow,ci_u[Source == "PML"] + ci_u[Source == "SIM"]))


bar_shallow <- drain_means_shallow %>% 
  ggplot(aes(DepthCat, mFrac*100))+
  geom_col(aes(fill = Source), position = position_stack(reverse = T)) +
  scale_fill_manual(values=c('#84c64d', '#409e93', '#4e6cb2'))+
  geom_errorbar(aes(ymin = ci_l*100, ymax = ci_u*100), width=0, 
                stat="identity")+
  coord_flip(ylim=c(0,100)) +
  geom_hline(yintercept=c(0,100))+
  facet_grid(Drainage~Season, scales="free")+
  theme_cowplot()+
  ylab("% Contribution")+
  xlab("")+
  ggtitle("station water depth <1m")+
  theme(strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        legend.position = "none")

```


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=9, fig.width=10}
drain_means_deep <- bind_cols(input,a2) %>% 
  pivot_longer(cols=SIM:PML, names_to = "Source") %>% 
  filter(Habitat=="Deep", !is.na(Drainage)) %>% 
  group_by(Drainage, DepthCat,Season, Source) %>% 
  summarize(mFrac=mean(value, na.rm=T), sdFrac=sd(value, na.rm=T), mDate=mean(Date_collected)) %>% 
  mutate(ci_l=mFrac-sdFrac, ci_u=mFrac+sdFrac, ci_l2=mFrac-sdFrac)


drain_means_deep$DepthCat = with(drain_means_deep, factor(DepthCat, levels = rev(levels(DepthCat))))

#change confidence interval location to go with stacked barplot
drain_means_deep$ci_l[drain_means_deep$Source == "PML"] <- with(drain_means_deep,ci_l[Source == "PML"] +
                                                        ci_l[Source == "MW"])
drain_means_deep$ci_u[drain_means_deep$Source == "PML"] <- with(drain_means_deep,ci_u[Source == "PML"] +
                                                        ci_u[Source == "MW"])
drain_means_deep$ci_l[drain_means_deep$Source == "SIM"] <- ifelse(drain_means_deep$mFrac[drain_means_deep$Source=="SIM"]<0, 0,
                                                        with(drain_means_deep,ci_l[Source == "PML"] +ci_l[Source == "SIM"]))
drain_means_deep$ci_u[drain_means_deep$Source == "SIM"] <- ifelse(drain_means_deep$mFrac[drain_means_deep$Source=="SIM"]<0, 0,
                                                        with(drain_means_deep,ci_u[Source == "PML"] + ci_u[Source == "SIM"]))


bar_deep <- drain_means_deep %>% 
  ggplot(aes(DepthCat, mFrac*100))+
  geom_col(aes(fill = Source), position = position_stack(reverse = T)) +
  scale_fill_manual(values=c('#84c64d', '#409e93', '#4e6cb2'))+
  geom_errorbar(aes(ymin = ci_l*100, ymax = ci_u*100), width=0, 
                stat="identity")+
  coord_flip(ylim=c(0,100)) +
  geom_hline(yintercept=c(0,100))+
  facet_grid(Drainage~Season, scales="free")+
  theme_cowplot()+
  ylab("% Contribution")+
  xlab("")+
  ggtitle("station water depth >2.5m")+
  theme(strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10))

plot_grid(bar_shallow,bar_deep, rel_widths = c(2.5,4))
```

##What have we learned?

* At break-up, both SIM and MW usually contribute to the large drops in salinity, but it varies by lagoon system
* Surface waters in deeper areas are quite similar to waters in shallow areas of each lagoon 
* Shallow areas of lagoons are mostly fresh water (from both MW and SIM)
* **Benthic environment in shallow areas of lagoons is heavily influenced by terrestrial runoff and sea ice melt compared to deeper areas ** 

***

#Other figures used in poster

```{r plotwnums, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

data_means %>% 
  filter(Habitat!="River", !is.na(Drainage)) %>% 
  group_by(Drainage, DepthCat, Season, Source) %>% 
  summarize(meanFrac=mean(mFrac))%>%
  ggplot(aes(DepthCat, meanFrac))+
  geom_col(aes(fill = Source), position = position_stack(reverse = TRUE)) +
  scale_fill_manual(values=c('#84c64d', '#409e93', '#4e6cb2'))+
  geom_text(aes(label = round(meanFrac*100)), size = 3, position = position_stack(vjust = 0.5))+ 
  geom_hline(yintercept=c(0,1))+
  coord_flip() +
  facet_grid(Drainage~Season, scales="free")+
  theme_cowplot()+
  ylab("")+
  xlab("mean contribution(%)")+
  theme(strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10))
```





##Salinity data vs timepoints of sampling


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=10}

pts <- ctd %>%
  right_join(data_means, by=c("station"="Station", "date"="mDate"))

mytheme <-theme(axis.text.x = element_text(angle = 45, hjust = 1, size=18),
        axis.text.y=element_text(size=18),
        axis.title=element_text(size=20),
        plot.title=element_text(size=24,face="bold"))


ctd_val <- ctd %>% filter(flags_condsal!="INV")%>%
  group_by(station, date) %>% 
  summarize(mSal=mean(salinity, na.rm=T)) 

ctd_val%>% 
  filter(station=="EELD2") %>% 
  ggplot(aes(date, mSal))+
  geom_line(size=1)+
  geom_vline(data=pts[pts$Drainage=="Elson East",], aes(xintercept=date), size=2, color='#2e2056', alpha=.5)+
  theme_cowplot()+
  ylim(c(0,45))+
  ylab("Salinity")+
  xlab("")+
  scale_x_date(breaks="2 months", date_labels="%b")+
  mytheme+
  ggtitle("Elson East")
  

ctd_val%>% 
  filter(station=="KALD2") %>% 
  ggplot(aes(date, mSal))+
  geom_line(size=1)+
  geom_vline(data=pts[pts$Lagoon=="Kakto",], aes(xintercept=date), size=1.5, color='#2e2056', alpha=.5)+
  theme_cowplot()+
  ylim(c(0,45))+
  ylab("Salinity")+
  xlab("")+
  scale_x_date(breaks="2 months", date_labels="%b")+
  mytheme+
  ggtitle("Kaktovik")

ctd_val%>% 
  filter(station=="JALD2") %>% 
  ggplot(aes(date, mSal))+
  geom_line(size=1)+
  geom_vline(data=pts[pts$Lagoon=="Jago",], aes(xintercept=date), size=1.5, color='#2e2056', alpha=.5)+
  theme_cowplot()+
  ylim(c(0,45))+
  ylab("Salinity")+
  xlab("")+
  scale_x_date(breaks="2 months", date_labels="%b")+
  mytheme+
  ggtitle("Jago")
```

mixing plot

```{r mixing_funtions, echo=FALSE, message=FALSE, warning=FALSE}

#create functions

mat <- data.frame("range_SIM" = c(0,0,100,75,75,50,50,25,25,
                                  10,10,10)/100,
                "range_MW" = c(100,0,0,25,0,50,0,75,0,
                               75,50,25)/100)


mat$range_PML <- abs(1-mat$range_SIM-mat$range_MW)


calc_s <- function(SIM, MW, PML){
  s <- (SIM*5)+(MW*0)+(PML*32.1)
  s
}

calc_o <- function(SIM, MW, PML,m){
  o <- (SIM*-2.5)+(MW*m)+(PML*-3.5)
  o
}

mixingplot <- function(m,lagoon){
  mat$sal <- calc_s(mat$range_SIM,mat$range_MW,mat$range_PML)
  mat$o18 <- calc_o(mat$range_SIM,mat$range_MW,mat$range_PML, m)
  
  mod_sim0 <-lm(mat$o18[mat$range_SIM==0]~mat$sal[mat$range_SIM==0]) 
  mod_sim25 <-lm(mat$o18[mat$range_SIM==.25]~mat$sal[mat$range_SIM==.25]) 
  mod_sim50 <-lm(mat$o18[mat$range_SIM==.50]~mat$sal[mat$range_SIM==.50]) 
  mod_sim75 <-lm(mat$o18[mat$range_SIM==.75]~mat$sal[mat$range_SIM==.75]) 
  
  SIMlab <- data.frame(y=c(-0.1,-0.1,-0.1,-0.1), x=c((-0.1-mod_sim0$coefficients[[1]])/mod_sim0$coefficients[[2]],                                                  (-0.1-mod_sim25$coefficients[[1]])/mod_sim25$coefficients[[2]],                                                     (-0.1-mod_sim50$coefficients[[1]])/mod_sim50$coefficients[[2]],                                                     (-0.1-mod_sim75$coefficients[[1]])/mod_sim75$coefficients[[2]]),
                       label = c("0%","25%","50%","75%"))
  
  mod_MW0 <-lm(mat$o18[mat$range_MW==0]~mat$sal[mat$range_MW==0]) 
  mod_MW25 <-lm(mat$o18[mat$range_MW==.25]~mat$sal[mat$range_MW==.25]) 
  mod_MW50 <-lm(mat$o18[mat$range_MW==.50]~mat$sal[mat$range_MW==.50]) 
  mod_MW75 <-lm(mat$o18[mat$range_MW==.75]~mat$sal[mat$range_MW==.75]) 
  
  MWlab <- data.frame(x=c(40,40,40,40), y=c(40*mod_MW0$coefficients[[2]]+mod_MW0$coefficients[[1]],
                                            40*mod_MW25$coefficients[[2]]+mod_MW25$coefficients[[1]],
                                            40*mod_MW50$coefficients[[2]]+mod_MW50$coefficients[[1]],
                                            40*mod_MW75$coefficients[[2]]+mod_MW75$coefficients[[1]]),
                      label = c("0%","25%","50%","75%"))
  
  ggplot(input[input$Lagoon==lagoon & input$Habitat!="River",], aes(Sal, delta_18O))+
    geom_abline(color="grey1", linetype=2,slope= mod_sim0$coefficients[[2]],intercept = mod_sim0$coefficients[[1]])+
    geom_abline(color="grey20", linetype=2,slope= mod_sim25$coefficients[[2]],intercept = mod_sim25$coefficients[[1]])+
    geom_abline(color="grey40", linetype=2,slope= mod_sim50$coefficients[[2]],intercept = mod_sim50$coefficients[[1]])+
    geom_abline(color="grey60", linetype=2,slope= mod_sim75$coefficients[[2]],intercept = mod_sim75$coefficients[[1]])+
    geom_abline(color="grey1",slope= mod_MW0$coefficients[[2]],intercept = mod_MW0$coefficients[[1]])+
    geom_abline(color="grey20",slope= mod_MW25$coefficients[[2]],intercept = mod_MW25$coefficients[[1]])+
    geom_abline(color="grey40",slope= mod_MW50$coefficients[[2]],intercept = mod_MW50$coefficients[[1]])+
    geom_abline(color="grey60",slope= mod_MW75$coefficients[[2]],intercept = mod_MW75$coefficients[[1]])+
    geom_text(data= MWlab, aes(x=x,y=y, label = label))+
    geom_text(data= SIMlab, aes(x=x,y=y, label = label))+
    geom_point(aes(color=Season, shape=DepthCat), size=4, alpha=0.8)+
    scale_color_manual(values=Pal[c(1,10,20)])+
    theme_cowplot()+
    scale_y_continuous(breaks=seq(-24,-4,4))+
    xlab("Salinity")+
    ylab(~ paste(delta ^ 18, "O ", ("%"[0])))+
    labs(shape="Sampling Depth")+
    theme(axis.text.y=element_text(size=18),
          axis.text.x=element_text(size=16),
          axis.title=element_text(size=20),
          plot.title=element_text(size=24,face="bold"))+
    panel_border()
  
  
}

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=6}
#plot
mixingplot(-12.9,"Elson")+
  ylim(c(-20,0))+
  xlim(c(0,40))+
  scale_y_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="   % meteoric water"))+
  scale_x_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="     % sea ice melt"))+
  ggtitle("Elson")

mixingplot(-17.35, "Simps")+
 ylim(c(-20,0))+
  xlim(c(0,40))+
  scale_y_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="   % meteoric water"))+
  scale_x_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="     % sea ice melt"))+
  ggtitle("Simpson")

mixingplot(-20.25, "Stef")+
  ylim(c(-20,0))+
  xlim(c(0,40))+
  scale_y_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="   % meteoric water"))+
  scale_x_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="     % sea ice melt"))+
  ggtitle("Stefansson Sound")

m <- mixingplot(-21.4, "Jago")

m+
  ylim(c(-20,0))+
  xlim(c(0,40))+
  geom_point(data=input[input$Lagoon=="Kakto",],aes(Sal, delta_18O, color=Season, shape=DepthCat), size=4, alpha=.7)+
  scale_y_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="   % meteoric water"))+
  scale_x_continuous(sec.axis=dup_axis(label=NULL, breaks=NULL, name="     % sea ice melt"))+
  ggtitle("Jago + Kaktovik")

# mixingplot(-21.4, "Kakto")+
#   ggtitle("Kaktovik")
```


